Illusion Game Validation (Study 1)

### 2022-08-05 study1.Rmd
edit instructions

>>>>

Perceptual decisions often exhibit a non-linear relationship with the objective physical values (e.g., a logarithmic relationship. In order to spread the difficulty levels based on the behavioral performance (to maximize the diversity of the stimuli in regards to perceptual processes), we generated, for study 2, stimuli with the difficulty levels spaced non-linearly, depending on the best underlying model (i.e., with an exponential, square or cubic spacing if the best model was *log*, *square root* or *cube root*). For instance, a linear space of [0.1, 0.3, 0.5, 0.7] can be transformed to an exponential space of [0.1, 0.27, 0.47, 0.7].
